### 2015-10-23 docs/prelim_analysis.Rmd
adds in new sims from IBM

Data and Methods
----------------
## Study sites and species
In the early 20th century, several range experiment stations in the western U.S. began mapping permanent quadrats, and conducted annual censuses for decades. 
We use such long-term demographic data sets from five semiarid grasslands in the western United States (described in detail by Chu and Adler 2015).
Each study site includes a set of $1-m^2$ permanent quadrats within which all individual plants were identified and mapped annually using a pantograph (Hill 1920).
The resulting mapped polygons represent basal cover for grasses and canopy cover for shrubs.
Data come from the Sonoran desert in Arizona (Anderson et al. 2012), sagebrush steppe in Idaho (Zachmann et al. 2010), southern mixed prairie in Kansas (Adler et al. 2007), northern mixed prairie in Montana (Anderson et al. 2011), and Chihuahuan desert in New Mexico (Anderson et al. in preparation, Chu and Adler 2015).

@@

Tables
------
```{r load_libs, echo=FALSE, message=FALSE}
library(communitySynchrony)
library(plyr)
library(reshape2)
library(synchrony)
library(ggplot2)
library(xtable)
library(gridExtra)
library(RColorBrewer)
```

@@

Figures
-------
```{r read_data, echo=FALSE}
output_list <- readRDS("../results/ipm_comp_nocomp_sims.RDS")
mlist <- melt(output_list)
```

```{r figure_1, echo=FALSE, fig.cap="Observed (vertical dashed lines) and IPM simulated (solid density curves) synchrony of species per capita growth rates based on changes in percent cover.", fig.width=6, fig.height=3}
nyrs <- c(max(out_az$stability$num_observations),
          max(out_id$stability$num_observations),
          max(out_ks$stability$num_observations),
          max(out_mt$stability$num_observations),
          max(out_nm$stability$num_observations))

@@

```{r figure_2, echo=FALSE, fig.cap="Results from IPM simulations with difference sources of stochasticity present/absent at each site. DEMO = demographic stochasticity only; ENV = environmental stochasticity only; ENVDEMO = both demograhpic and environmental stochasticity.", fig.width=6}
colnames(mlist)[1:3] <- c("year", "species", "cover")
sites <- unique(mlist$L1)
sims <- unique(mlist$L2)
pgr_list <- list()
for(dosite in sites){
  tmp_data <- subset(mlist, L1==dosite)
  if(dosite=="Idaho"){
    tmp_data <- subset(tmp_data, species!="ARTR")
  }
  within_site_list <- list()
  for(dosim in sims){
    tmpsim <- subset(tmp_data, L2==dosim)[c("year", "species", "cover")]
    tmpsynch <- get_ipm_synchrony(tmpsim)
    tmp_pgr_synch <- as.numeric(tmpsynch$pgr_synchrony["obs"])
    within_site_list[[dosim]] <- tmp_pgr_synch
  }
  pgr_list[[dosite]] <- within_site_list
}
pgr_synch <- melt(pgr_list)
expected_synch <- table_data[,c(1,3)]
expected_synch$L2 <- "E(SYNCH)"
colnames(expected_synch) <- c("L1", "value", "L2")
expected_synch <- expected_synch[,c("value", "L2", "L1")]
expected_synch[which(expected_synch[,"L1"]=="New Mexico"),"L1"] <- "NewMexico"

@@

Additional Figures
------------------
```{r time_series, eval=FALSE, echo=FALSE, fig.cap="Example time series from the simulations."}
ggplot(mlist, aes(x=year, y=(cover*100), color=species))+
  geom_line()+
  facet_grid(L1~L2, scale="free")
```

>>>>

Data and Methods
----------------
## Study sites and species
In the early 20th century, several range experiment stations in the western U.S. began mapping permanent quadrats, and conducted annual censuses for decades. 
We use such long-term demographic data sets from five semiarid grasslands in the western United States (described in detail by Chu and Adler 2015).
Each study site includes a set of 1-$\text{m}^2$ permanent quadrats within which all individual plants were identified and mapped annually using a pantograph (Hill 1920).
The resulting mapped polygons represent basal cover for grasses and canopy cover for shrubs.
Data come from the Sonoran desert in Arizona (Anderson et al. 2012), sagebrush steppe in Idaho (Zachmann et al. 2010), southern mixed prairie in Kansas (Adler et al. 2007), northern mixed prairie in Montana (Anderson et al. 2011), and Chihuahuan desert in New Mexico (Anderson et al. in preparation, Chu and Adler 2015).

@@

Tables
------

\singlespacing

Table 1: Site descriptions and focal species.
\footnotesize

| Site Name | Biome | Location (Lat, Lon) | Obs. Years | Species |
| --------- | ----- | ------------------- | ---------- | ------- |
| Arizona | Sonoran Desert | 31&deg;50' N, 110&deg;53' W | 1915-1933 | *Bouteloua eriopoda* |
| | | | | *Bouteloua rothrockii* |
| Idaho | Sagebrush steppe | 44.2&deg; N, 112.1&deg; W | 1926-1957 | *Artemisia tripartita* |
| | | | | *Pseudoroegneria spicata* |
| | | | | *Hesperostipa comata* |
| | | | | *Poa secunda* |
| Kansas | Southern mixed prairie | 38.8&deg; N, 99.3&deg; W | 1932-1972 | *Bouteloua curtipendula* |
| | | | | *Bouteloua hirsuta* |
| | | | | *Schizachyrium scoparium* |
| Montana | Northern mixed prairie | 46&deg;19' N, 105&deg;48' W | 1926-1957 | *Bouteloua gracilis* |
| | | | | *Hesperostipa comata* |
| | | | | *Pascopyrum smithii* |
| | | | | *Poa secunda* |
| New Mexico | Chihuahuan Desert | 32.62&deg; N, 106.67&deg; W | 1915-1950 | *Bouteloua eriopoda* |
| | | | | *Sporobolus flexuosus* |

```{r load_libs, echo=FALSE, message=FALSE, warning=FALSE}
library(communitySynchrony)
library(plyr)
library(reshape2)
library(synchrony)
library(ggplot2)
library(xtable)
library(gridExtra)
library(RColorBrewer)
```

@@

Figures
-------
```{r read_data, echo=FALSE, eval=F}
output_list <- readRDS("../results/ipm_comp_nocomp_sims.RDS")
mlist <- melt(output_list)
```

```{r figure_1, echo=FALSE, fig.cap="Observed (vertical dashed lines) and IPM simulated (solid density curves) synchrony of species per capita growth rates based on changes in percent cover.", fig.width=6, fig.height=3, eval=F}
nyrs <- c(max(out_az$stability$num_observations),
          max(out_id$stability$num_observations),
          max(out_ks$stability$num_observations),
          max(out_mt$stability$num_observations),
          max(out_nm$stability$num_observations))

@@

```{r figure_2, echo=FALSE, fig.cap="Results from IPM simulations with difference sources of stochasticity present/absent at each site. DEMO = demographic stochasticity only; ENV = environmental stochasticity only; ENVDEMO = both demograhpic and environmental stochasticity.", fig.width=6, eval=F}
colnames(mlist)[1:3] <- c("year", "species", "cover")
sites <- unique(mlist$L1)
sims <- unique(mlist$L2)
pgr_list <- list()
for(dosite in sites){
  tmp_data <- subset(mlist, L1==dosite)
  if(dosite=="Idaho"){
    tmp_data <- subset(tmp_data, species!="ARTR")
  }
  within_site_list <- list()
  for(dosim in sims){
    tmpsim <- subset(tmp_data, L2==dosim)[c("year", "species", "cover")]
    tmpsynch <- get_ipm_synchrony(tmpsim)
    tmp_pgr_synch <- as.numeric(tmpsynch$pgr_synchrony["obs"])
    within_site_list[[dosim]] <- tmp_pgr_synch
  }
  pgr_list[[dosite]] <- within_site_list
}
pgr_synch <- melt(pgr_list)
expected_synch <- table_data[,c(1,3)]
expected_synch$L2 <- "E(SYNCH)"
colnames(expected_synch) <- c("L1", "value", "L2")
expected_synch <- expected_synch[,c("value", "L2", "L1")]
expected_synch[which(expected_synch[,"L1"]=="New Mexico"),"L1"] <- "NewMexico"

@@

Additional Figures
------------------
```{r time_series, eval=FALSE, echo=FALSE, fig.cap="Example time series from the simulations.", eval=F}
ggplot(mlist, aes(x=year, y=(cover*100), color=species))+
  geom_line()+
  facet_grid(L1~L2, scale="free")
```
